\documentclass[11pt, a4paper]{article}
\usepackage{fontspec} 

% DOCUMENT LAYOUT
\usepackage{geometry} 
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in, top=0.5in, left=0.8in, right=0.8in, bottom=0.5in}
\setlength\parindent{0in}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont [Ligatures={Common}, Numbers={OldStyle}]{Hoefler Text}
\setmonofont[Scale=0.8]{Monaco} 
\setsansfont[Scale=0.9]{Optima Regular}
\newcommand{\amper}{{\fontspec[Scale=.95]{Hoefler Text}\selectfont\itshape\&}}
\usepackage{marginnote}
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\sffamily\mdseries\Large\underline} 
\subsectionfont{\rmfamily\mdseries\scshape\normalsize} 
\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize} 
\pagestyle{empty}

\newlength{\wideitemsep}
\setlength{\wideitemsep}{-2pt}
%\addtolength{\wideitemsep}{-1pt}
\let\olditem\item
\renewcommand{\item}{\setlength{\itemsep}{\wideitemsep}\olditem}

\linespread{0.9}

\begin{document}

\textsf{\centering{\Huge Jakub Dominik Koz\l owski}\\[0.1in]}

%\begin{minipage}[b]{2in}
%\small{mobile: 07846707813}
%\end{minipage}
%\begin{minipage}[b]{2in}
%\centering{\small{email: mail@jakub-kozlowski.com}}
%\end{minipage}
%\begin{minipage}[b]{2.5in}
%\begin{flushright}\small{github: github.com/jkozlowski}\end{flushright}
%\end{minipage}

\section*{Skills}
\begin{itemize}
\item \textbf{Java}: 4 years; JEE6 APIs: JPA, JAXB, JAX-RS, EJB – Summer 2010.
\item \textbf{Scala}: since Sept 2012, completed \textbf{Functional Programming Principles in Scala} course organised by Martin Odersky; \textbf{scalaz} 
\item \textbf{Haskell}: since Jan 2014.
\item \textbf{Hibernate, Glassfish, OSGi, Hadoop}.
\item \textbf{Test-Driven Development, OOP, Design Patterns, Functional Programming.}
\item \textbf{Open Source Development Tools}: Maven3, Jenkins, TestNG, Git.
\end{itemize}

\section*{Experience}

\paragraph{Sept 2014, Open Source,  \textit{http://github.com/jkozlowski/kdb-haskell}.}
\begin{itemize}
\item Working on Haskell client library to kdb+ database. 
\end{itemize}

\paragraph{January 2013, IT Graduate in Cash Equities, Algo Development Team, UBS.}
\begin{itemize}
\item Rewrite of an algo decision engine on top of Akka in order to improve testability and enable full message persistence to a KDB database for debugging/recovery purposes. 
\end{itemize}

\paragraph{September 2012, IT Graduate in Cash Equities, Cash Automation Team, UBS.}
\begin{itemize}
\item Finished a rewrite of a network latency visualisation tool with RESTful back end talking to a KDB database and AJAX/HTML5 front-end.  
\end{itemize}

\paragraph{MEng, Final Year Project, Eugene: Agent-Based Market Simulator for use in Validation and System Testing of Trading Algorithms.} 
\begin{itemize}\item Explores the efficacy of using Agent-Based Simulation for testing of Trading Algorithms that could supplement backtesting on historical data.
\item Received a distinction - 86\%.
\item Awarded second place in \textit{IBM Individual Project Prize 2011/2012}.
\end{itemize}

\paragraph{March 2012, An Analysis of Distributed Indexing, Group Project, Information Retrieval and Data Mining.}
\begin{itemize}
\item An investigation into the viability of distributed indexing with Terrier, performed using a Hadoop cluster (Cloudera distribution) on a subset of ClueWeb09B corpus (approx. 14GB compressed data).
\item Awarded Bronze Award at StuConOS, the 1st Student Conference on Optimisation of Software at UCL.
\end{itemize}

\paragraph{Summer 2011, Summer Internship, UBS.}
\begin{itemize}
\item Implemented a framework for automatic migration of legacy Groovy code to a new API.\item Mentored a group of Work Experience personnel to help with Automated Testing of Trading Algorithms through simulation.
\end{itemize}

\paragraph{October 2010 – March 2011, Newton Spectrum Browser, 3rd Year University Group Project.}
\begin{itemize}
\item Successfully led a team of 3 developers that delivered a manuscript browser to display and visualize documents stored in TEI format.\item Responsible for planning iterations, designing the overall architecture of the software and implementing crucial modules. 
\item Received a distinction - 80\%.
\end{itemize}

\paragraph{Summer 2010 – 15 week Internship, CiteSeeing – citeseeing.com, Ingemar Cox, University College London.}
\begin{itemize}
\item As member of a two-programmer team, successfully completed design and implementation of a web service that provides citation information about published academic papers. Ensured team productivity and rapid development by employing JEE6 stack with Glassfishv3.\item Co-Implemented a document fingerprinting algorithm, following Design Patterns. Designed and implemented persistence layer using EJB and JPA APIs with Hibernate provider.\item Designed and implemented RESTful API using JAX-WS and JAXB.
\end{itemize}

\section*{Education}
\paragraph{2008 – 2012, University College London, MEng Computer Science.}
\begin{itemize}
\item Awarded First Class Honours Degree.
\item Excellent overall results for 1st (74\%), 2nd (76.88\%), 3rd (79.13\%) and 4th (82.5\%) academic years.\item Received Wiley Book Prize for best performance in practical subjects for 3rd year.\item Awarded Dean's List certificate in recognition of outstanding academic achievements for 2nd, 3rd and 4rth year.\item Received Computer Science Department Sessional Prize for academic achievements for 1st year.\item Obtained 3 year MISYS Scholarship for academic excellence.\item Master Level modules: Financial Markets and Financial Information Systems, as well as Distributed Computing and Security, and Information Retrieval and Data Mining.
\end{itemize}


\end{document}
